---
title: "CLT_WUP"
author: "Renelyn Wilson"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

kkardashtemp  see code below

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")

my1000 <- sample(Homers_data , size = 1000, replace=T)

```




```{r}

library(ggplot2)
sampleNumber = sample(1:10000, size = 1000)
library(dplyr)
my1000 <- Homers_data[sampleNumber, ]
names(my1000)
# Basic density
p <- ggplot(my1000, aes(x=kkardashtemp,col=sex)) + 
  geom_density()
p
# Add mean line
p+ geom_vline(aes(xintercept=mean(kkardashtemp)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$kkardashtemp),' sd = ',sd(my1000$kkardashtemp)))
```


In our original and set standard deviation when deciding on kkardashtemp and how male and female view kim kardashion's attractiveness. Many of the female voted very low in the opinion of kkardashtemp and many male voted in favor of her.  When we put in numb 9 it looks like when rating kkarrdashtemp there is a higher uptake in male than female, with female being very close to zero and male being very close to 100.   
When our numb is 16 I believe our standard deviation will be around 10.4 
```{r}
numb=16
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k16 = x.avg

p <- ggplot(my1000, aes(x=k16)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k16)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k16),' sd = ',sd(my1000$k16)))

```

With numb 9 we can observe that there is a peak with MF both influencing each other and being more towards the left, the lesser side on the kkardashtemp scale. When trying numb 16 the sd is about 10.1 and the curve of the voting is becoming less varied and more rounded out with a lean to the right which is where they are in favor of kkardashttemp. 

## We expect the sample mean to be close to population and the standev to get smaller by the ratio of one to the sample size. In this case 1/sqrt(2)

### There are 3 peaks in the density plot. You pick two people you can get MM,MF.FM,or FF. these are all equally likey so the little peak on left is all the FF's while the little peak on the right is all the MM's so the big one in the middle is both the MF and FM in the same bag so-to-speak.  



```{r}
numb = 16
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k16 = x.avg


p <- ggplot(my1000, aes(x=k16),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k16)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 4") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k16),' sd = ',sd(my1000$k16)))

```


### In this case the stdev was cut in half because the sample size was four. This is what the central limit theorem says. There are also 5 peaks. They go from FFFF,to FFFM, to FFMM to FMMM and finally MMMM.

# Now finish by adding blocks with numb being 9, then 16, 25, and 36. be sure to mention how the standard deviation progresses as the sample size changes,

Unlike before the graph was more varied this graph with our new standard deviation about 14 with the numb 9 is more blended in with smaller loops than the dipping five we use to see. With the numb 16 the graph looks to be less leaning towards anywhere and more coming to a consensus in the middle and to a peak but it is still more towards the right. 
